Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating and Growing

### 2017-10-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
improved figures/Buffer_ThreeKinds.pdf
improved the authors of some references; balanced the two columns of references at the last page
removed tex files of a branch version
improved some codes
moved a tikz figure to ipe figures/NumberOfBuildings.pdf
added file about copyright

\documentclass[sigconf, authordraft]{acmart}

@@

\usepackage{booktabs} % For formal tables
\usepackage{xspace}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{tikz,pgfplots}
\pgfplotsset{compat=1.3} %make y lable compact in a tikz picture with axes

@@

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Figure~}
\newcommand{\eq}{Equation~}
\newcommand{\sect}{Section~}
\newcommand{\tab}{Table~}
\newcommand{\figs}{Figures~}
\newcommand{\eqs}{Equations~}
\newcommand{\sects}{Sections~}
\newcommand{\tabs}{Tables~}
\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[UrbanGIS'17]{International Workshop on Smart Cities and Urban 
Analytics}{November 2017}{Redondo Beach, California USA} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{15.00}

\acmSubmissionID{123-A12-B3}

@@

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Chair of Computer Science I, University of W\"urzburg}
  \streetaddress{Am Hubland}
  \city{W\"urzburg} 
  \state{Germany} 
  \postcode{97074}
}
\email{dongliang.peng@uni-wuerzburg.de}

@@

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{References}

>>>>

\documentclass[
sigconf,
screen, %hyperlinks are colored
%authorversion,
%authordraft %Whether author’s draft mode is enabled
]{acmart}

@@

\usepackage{booktabs} % For formal tables
\usepackage{xspace}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption,disable]{todonotes}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{balance}
%\usepackage{tikz,pgfplots}
%\pgfplotsset{compat=1.3} %make y lable compact in a tikz 
%%picture with axes

@@

\newcommand{\fig}{Figure~}
\newcommand{\eq}{Equation~}
\newcommand{\sect}{Section~}
\newcommand{\tab}{Table~}
\newcommand{\figs}{Figures~}
\newcommand{\eqs}{Equations~}
\newcommand{\sects}{Sections~}
\newcommand{\tabs}{Tables~}
\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, 
t\ifthenelse{\equal{#1}{}}{}{_#1}}}

@@

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{0000-0001-6848-3545}
\affiliation{%
  \institution{Chair of Computer Science I, University of W\"urzburg}
  \streetaddress{Am Hubland}
  \city{W\"urzburg} 
  \state{Germany} 
  \postcode{97074}
}
\email{dongliang.peng@uni-wuerzburg.de}

@@

\copyrightyear{2017}
\acmYear{2017}
\setcopyright{othergov}
\acmConference[UrbanGIS'17]{UrbanGIS'17:3rd ACM SIGSPATIAL 
	Workshop on Smart Cities and Urban Analytics }{November 
	7--10, 
	2017}{Redondo Beach, CA, USA}
\acmBooktitle{UrbanGIS'17: UrbanGIS'17:3rd ACM SIGSPATIAL 
	Workshop on Smart Cities and Urban Analytics , November 
	7--10, 
	2017, Redondo Beach, CA, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3152178.3152188}
\acmISBN{978-1-4503-5495-0/17/11}

@@

\bibliographystyle{ACM-Reference-Format}
\balance %balance the two columns of references at the last page
\bibliography{References}
